Open archaeology, open source?

### 2023-09-19 analysis/_03-data_methodology.qmd
Get repo info from GH API
Incl. licenses

```{r data-github}
# If cached data at `analysis/data/derived_data/oarch.RData` is present, this
# chunk will prefer to load it rather than make requests to the GitHub API.
# Delete this file to fetch fresh data from the GitHub or modify 
# `cached_gh_data` to read a different cached version.
#
# Note that fetching data from the GitHub API takes some time and is subject to
# a rate limit:
# <https://docs.github.com/en/rest/overview/resources-in-the-rest-api#rate-limiting>
#
# You will need to authenticate authenticate with GitHub credentials to get a
# rate limit sufficient to obtain the required data, see 
# <https://gh.r-lib.org/articles/managing-personal-access-tokens.html>
# for options on how to do this.
cached_gh_data <- here("analysis/data/derived_data/oarch.RData")
if (!file_exists(cached_gh_data)) {
  oarch <- mutate(oarch,
                  gh_langs = map(oarch$gh_repo, gh_lang),
                  gh_contribs = map(oarch$gh_repo, gh_contrib),
                  gh_issues = map(oarch$gh_repo, gh_issue),
                  gh_comments = map(oarch$gh_repo, gh_comment),
                  gh_commits = map(oarch$gh_repo, gh_commit)
  )
  saveRDS(oarch, cached_gh_data)
}
oarch <- readRDS(cached_gh_data)
```

@@

**NOTE:** Add a breakdown on licensing practices.

>>>>

```{r data-github}
# If cached data at `analysis/data/derived_data/oarch.RData` is present, this
# chunk will prefer to load it rather than make requests to the GitHub API.
# Delete this file to fetch fresh data from the GitHub or modify 
# `cached_gh_data` to read a different cached version.
#
# Note that fetching data from the GitHub API takes some time and is subject to
# a rate limit:
# <https://docs.github.com/en/rest/overview/resources-in-the-rest-api#rate-limiting>
#
# You will need to authenticate authenticate with GitHub credentials to get a
# rate limit sufficient to obtain the required data, see 
# <https://gh.r-lib.org/articles/managing-personal-access-tokens.html>
# for options on how to do this.
cached_gh_data <- here("analysis/data/derived_data/oarch.RData")
if (!file_exists(cached_gh_data)) {
  oarch <- mutate(oarch,
                  gh_repo_info = map(gh_repo, gh_repo_info, .progress = TRUE),
                  gh_langs = map(gh_repo, gh_lang, .progress = TRUE),
                  gh_contribs = map(gh_repo, gh_contrib, .progress = TRUE),
                  gh_issues = map(gh_repo, gh_issue, .progress = TRUE),
                  gh_comments = map(gh_repo, gh_comment, .progress = TRUE),
                  gh_commits = map(gh_repo, gh_commit, .progress = TRUE),
  )
  saveRDS(oarch, cached_gh_data)
}
oarch <- readRDS(cached_gh_data)
```

@@

**NOTE:** Add a breakdown on licensing practices.
```{r tbl-repo-licenses}
```
